---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
  [![R-CMD-check](https://github.com/fragla/rheumtools/actions/workflows/check-standard.yaml/badge.svg)]
<!-- badges: end -->

# rheumtools

The goal of rheumtools is to provide a collection of functions that can help in the analysis of clinical rheumatology data. These include methods for calculating disease activity scores such as `basdai_score()`, `das_28_esr_score()` and `dapsa_score()` as well as methods for categorising disease activity and calculating response to treatment. Other generic methods, such as `body_mass_index()` and `percentage_response()` are also included.

## Installation

You can install the development version of rheumtools from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("fragla/rheumtools")
```

## Example

Calculation of disease activity using DAS28-ESR.

```{r example}
library(rheumtools)

#DAS28-ESR
das1 <- das_28_esr_score(tjc = 6, sjc = 5, esr = 22, ptgh = 85)
das1

das2 <- das_28_esr_score(tjc = 1, sjc = 1, esr = 10, ptgh = 39)
das2

#Classification
das_28_classification(das1)
das_28_classification(das2)

#Response
eular_ra_response(das1, das2)

#The functions are also vectorised so disease activity and classification could be calculated using
das <- das_28_esr_score(tjc = c(6,1), sjc = c(5,1), esr = c(22,10), ptgh = c(85,39))
das

das_28_classification(das)

```

## License

This project is licensed under the MIT License - see the [LICENSE.md](https://github.com/fragla/rheumtools/blob/main/LICENSE.md) file for details.
